GLMM

### 2024-06-13 Code/GLMM.Rmd
added 100m dash

>>>>

### 18
We now examine the men's 100 meter dash times from 1999 to 2023.
```{r}
times <- read.csv("../Data/GLMMData.csv")
colnames(times) <- c("Venue", "Type", "Time", "RxnTime", "Gender", "Heat", "Event")
dash_2022 <- subset(times, (Type == "F" | Type == "S") & Gender == "M" & (Time != 'DQ' | Time != "DNS")
                   & Event == "Dash")
dash_no_2022 <- subset(times, (Type == "F" | Type == "S") & Gender == "M" & (Time != 'DQ' | Time != "DNS")
                   & Event == "Dash" & Venue != 2022)
```

```{r}
library(tidyverse)
dash_2022 <- times |>
  filter(Type == "F" | Type == "S") |>
  filter(Gender == "M") |>
  filter(Time != "DNS") |>
  filter(RxnTime != 0) |>
  mutate(RxnTime = ifelse(RxnTime < 0.1, 0.1, RxnTime))

dash_no_2022 <- times |>
  filter(Venue != 2022) |>
  filter(Type == "F" | Type == "S") |>
  filter(Gender == "M") |>
  filter(Time != "DNS") |>
  filter(RxnTime != 0) |>
  mutate(RxnTime = ifelse(RxnTime < 0.1, 0.1, RxnTime))
```

### 19
Baseline models
```{r}
library(lme4)
dash_no_2022_one_gamma_log <- glm(RxnTime ~ 1, data = dash_no_2022, 
                                    family = Gamma(link = "log"))
dash_2022_one_gamma_log <- glm(RxnTime ~ 1, data = dash_2022, 
                                family = Gamma(link = "log"))
```

### 20
This code creates the venue effect only models.
```{r}
dash_no_20222022_venue_gamma_log <- glmer(RxnTime ~ (1|Venue), data = dash_no_2022, 
                                       family = Gamma(link = "log"))
dash_2022_venue_gamma_log <- glmer(RxnTime ~ (1|Venue), data = dash_2022, 
                                   family = Gamma(link = "log"))
```

### 21
This creates the heat effect only models.
```{r}
dash_no_2022_heat_gamma_log <-glmer(RxnTime ~ (1 | Heat), data = dash_no_2022, 
                             family = Gamma(link = "log"))
dash_2022_heat_gamma_log <-glmer(RxnTime ~ (1 | Heat), data = dash_2022, 
                         family = Gamma(link = "log"))
```

### 22
This creates the models with a venue effect and heat effect.
```{r}
dash_no_2022_two_effect_gamma_log <- glmer(RxnTime ~ (1 | Venue) + (1 | Heat), 
                                   data = dash_no_2022,
                                   family = Gamma(link = "log"))
dash_2022_two_effect_gamma_log <- glmer(RxnTime ~ (1 | Venue) + (1 | Heat), 
                               data = dash_2022,
                               family = Gamma(link = "log"))
```

### 23
Now we test
```{r}
sim_two_effect_time(dash_no_2022_two_effect_gamma_log,
                    dash_no_2022_one_gamma_log, 0.1)
sim_two_effect_time(dash_2022_two_effect_gamma_log,
                    dash_2022_one_gamma_log, 0.1)
```
